Self Regulation Ontology Retest Analyses

### 2018-08-15 code/SRO_Retest_Analyses.Rmd
refactored the retest stats scripts for ddm analyses
added updated graphs

theme_set(theme_bw())

@@

ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+

  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_shape_manual(values = c(0:9),
                     breaks = c("acc_icc", "avg_rt_icc", "conceptual_responses_icc", "fail_to_maintain_set_icc", "learning_rate_icc", "learning_to_learn_icc", "nonperseverative_errors_icc", "perseverative_errors_icc", "perseverative_responses_icc", "total_errors_icc"),
                     labels = c("Accuracy", "Average Response Time", "Conceptual Responses", "Failure to Maintain Set", "Learning Rate", "Learning to Learn",  "Nonperseverative Errors", "Perseverative Errors", "Perseverative Responses", "Total Errors"))

@@

```{r}
ddm_boot_plot = tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=12),
        strip.text = element_text(size=12),
        axis.text = element_text(size = 12),
        text = element_text(size=12))+
  guides(fill = guide_legend(ncol = 2, byrow=F))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))

>>>>

@@

ggsave('LitAndEmpAveCor.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 4, height = 4, units = "in", limitsize = FALSE, dpi = 500)
```

@@

trial_num_rel_df %>%
  gather(key, value, -breaks) %>%
  filter(key %in% c("avg_rt_icc", "learning_to_learn_icc", "nonperseverative_errors_icc")) %>%
  ggplot(aes((breaks+1)*10, value, shape=key))+
  geom_point()+
  geom_line(alpha = 0.5)+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom')+
  scale_shape_manual(values = c(0:9),
                     breaks = c("avg_rt_icc","learning_to_learn_icc", "nonperseverative_errors_icc"),
                     labels = c("Average Response Time", "Learning to Learn",  "Nonperseverative Errors"))

@@

```{r}
ddm_boot_plot = tmp %>%
  group_by(dv) %>%
  summarise(mean_icc = mean(icc),
            raw_fit = unique(raw_fit),
            contrast = unique(contrast),
            rt_acc = unique(rt_acc)) %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), mean_icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2, byrow=F))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))
